Research Cases

### 2025-10-12 Code/R/Research/cases_research.Rmd
more sum of periodics cases research

```{r}
calc_errors <- function(R, pred_func, err_func, signal, seed = 5) {
  with(plan(multisession), {
    batch_recs <- function(R) {
      p <- progressor(R)
      future_replicate(R, {
        p()
        pred_func()
      }, simplify = "array", future.seed = seed)
    }
    if (sd == 0)
      recs <- batch_recs(2) # don't need R because no noise present. Set to 2, because with 1 will be simplified
    else
      recs <- batch_recs(R)
  })

@@

# params_grid_list: list with the parameter names as names and vectors of the parameters values as values
calc_errors_by_params <- function(params_grid_list, R, comp_func, err_func, signal, seed = 5) {
  params_grid <- expand.grid(params_grid_list)
  results <- params_grid
  results$error <- numeric(nrow(params_grid))
  for (i in seq(nrow(params_grid))) {
    print(paste0(names(params_grid), " = ", params_grid[i,], collapse = ", "))
    list2env(params_grid[i,], envir = parent.frame())
    results[i,]$error <- calc_errors(R, comp_func, err_func, signal, seed)
  }
  return(results)
}
```

@@

# Two periodics case
## Short series
```{r}
# no rates
# rates.true <- c(0, 0)
# rates_case <- "_nr"
# small equal rated
# rates.true <- c(-0.01, -0.01)
# plot.name <- "_ser"
# large equal rates
# rates.true <- c(-0.02, -0.02)
# plot.name <- "_ler"
# different rated
rates.true <- c(-0.01, -0.02)
rates_case <- "_dr"

@@

full_case <- paste0(rates_case, freqs_case, A_case, phases_case, complex_case)

max.r <- calc_rank(A, rates.true, freqs.true, phases.true, complex.signal)

N <- 25
stopifnot(N > max.r * 2 + 1)
signal <- construct_periodics(N, A, rates.true, freqs.true, phases.true, complex.signal)

groups_ssa <- list(1:max.r)
Ls_ssa <- seq(from = max.r + 1,
              to = (N + 1) %/% 2,
              by = 1)

@@

# I >= L >= J
Is_tmp <- seq(from = max.r + 1,
          to = N - max.r - 1,
          by = 1)
Ls_tmp <- seq(from = max.r + 1,
          to = N - max.r - 1,
          by = 1)

correct.dims <- which(outer(Is_tmp, Ls_tmp, (\(i, l) ifelse((i >= l) &
                                                      (N - i - l + 2 > max.r) &
                                                      (N - i - l + 2 <= l), TRUE, FALSE
))), arr.ind = TRUE)

>>>>

```{r}
calc_errors <- function(R, pred_func, err_func, signal, seed = 5) {
  with(plan(multisession), {
    batch_recs <- function(R) {
      # p <- progressor(R)
      future_replicate(R, {
        # p()
        pred_func()
      }, simplify = "array", future.seed = seed)
    }
    if (sd == 0)
      recs <- batch_recs(2) # don't need R because no noise present. Set to 2, because with 1 will be simplified
    else
      recs <- batch_recs(R)
  })

@@

# params_grid_list: list with the parameter names as names and vectors of the parameters values as values
calc_errors_by_params <- function(params_grid_list, R, comp_func, err_func, signal, seed = 5) {
  params_grid <- expand.grid(params_grid_list)
  results <- params_grid
  results$error <- numeric(nrow(params_grid))
  q <- progressor(nrow(params_grid))
  for (i in seq(nrow(params_grid))) {
    # print(paste0(names(params_grid), " = ", params_grid[i,], collapse = ", "))
    list2env(params_grid[i,], envir = parent.frame())
    results[i,]$error <- calc_errors(R, comp_func, err_func, signal, seed)
    q()
  }
  return(results)
}
```

@@

# Two periodics case
## Short series
```{r}
# no rates
rates.true <- c(0, 0)
rates_case <- "_nr"
# small equal rated
# rates.true <- c(-0.01, -0.01)
# rates_case <- "_ser"
# large equal rates
# rates.true <- c(-0.02, -0.02)
# rates_case <- "_ler"
# different rated
# rates.true <- c(-0.01, -0.02)
# rates_case <- "_dr"

@@

# N <- 25
# n_case <- ""
N <- 100
n_case <- "_long"

full_case <- paste0(n_case, rates_case, freqs_case, A_case, phases_case, complex_case)
max.r <- calc_rank(A, rates.true, freqs.true, phases.true, complex.signal)

stopifnot(N > max.r * 2 + 1)
signal <- construct_periodics(N, A, rates.true, freqs.true, phases.true, complex.signal)

groups_ssa <- list(1:max.r)

if (n_case == "") {
  Ls_ssa <- seq(from = max.r + 1,
                to = (N + 1) %/% 2,
                by = 1)
} else {
  Ls_ssa <- seq(from = max.r + 1,
                to = (N + 1) %/% 2,
                by = 5)
}

@@

# I >= L >= J
if (n_case == "") {
  Is_tmp <- seq(from = max.r + 1,
                to = N - max.r - 1,
                by = 1)
  Ls_tmp <- seq(from = max.r + 1,
                to = N - max.r - 1,
                by = 1)
} else {
  Is_tmp <- seq(from = max.r + 1,
                to = N - max.r - 1,
                by = 5)
  Ls_tmp <- seq(from = max.r + 1,
                to = N - max.r - 1,
                by = 5)
}
correct.dims <- which(outer(Is_tmp, Ls_tmp, (\(i, l) ifelse((i >= l) &
                                                      (N - i - l + 2 > max.r) &
                                                      (N - i - l + 2 <= l), TRUE, FALSE
))), arr.ind = TRUE)
